---
title: "Package Developement"
date: "6/11/2018"
output: html_document
---


<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}

  }
td {  /* Table  */
  font-size: 8px;
  
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 30px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 25px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  background: #cce5ff;
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}

ol { /* ordered list style */
    font-size: 20px;font-weight:bold;}

ul {/* dot list style */
font-size: 15px;}


</style>


## Package development
### One way of developing R packages is using the devtools package, and usethis package. 


1. create a r file that will bag functions for the packages
```{r eval=F }
  usethis::use_r('RfileName')
```

2. save existing data (called df, for example) into a data directory (It will create a directory if not available yet)
```{r eval=F}
devtools::use_data(df,overwrite = TRUE)
```
 
3. automate documentation after insert roxygen skeleton into each function (Ctrl + shift + Alt + R)
```{r eval=F}
devtools::document()
```
 
4. automate documentation for internal data (detail skipped)
```{r eval=F}
devtools::use_data_raw()
```

5. create a rmarkdown file for automate md file for github
```{r eval=F}
devtools::use_readme_rmd()
```

6. refresh all (r) files in the package before testing all functions within the package
```{r eval=F}
devtools::load_all('.')
```

7. install the package from the source (package could be saved in github as well)
```{r eval=F}
devtools::install(RfileName)
```




