---
title: "Priviate Repository"
date: "6/11/2018"
output: html_document
---


<style type="text/css">

.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
td {  /* Table  */
  font-size: 8px;
  
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 30px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 25px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  background: #cce5ff;
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}

ol { /* ordered list style */
    font-size: 20px;font-weight:bold;}

ul {/* dot list style */
font-size: 15px;
}


</style>




## Private Repository
### After building packages in local drive, you may want to share it within the same rstudio server or inbetween R-connect and Rstudio Server. Having a local private repository could be one of the solutions. 

1. Putting devtolls package into local repository (for example, adding a package called 'ERMdata' in  to private repository) -
```{r eval=FALSE}
miniCRAN::addLocalPackage(pkgs = 'ERMdata',pkgPath = '../../Packages Development/2018/',path= '/DataERMUsers/ERMrepository/', build=T)
```

2. In addtion, you may want to include the local repository location in the .Rprofile if you would like to set it as one of default repositories (eg. packrat in Rconnect applications will know where to grab the package) or - 
```{r eval= FALSE}
local({
  r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/"
  r["ERMrepository"] <- "file://DataERMUsers/ERMrepository"
  options(repos = r)
})
```





