---
title: "Package Repository"

output: html_document
---

<link href="style/styleRepo.css" rel="stylesheet">



## Private Repository
### After building packages in local drive, you may want to share it within the same rstudio server or inbetween R-connect and Rstudio Server. Having a local private repository could be one of the solutions. 

* Putting devtolls package into local repository (for example, adding a package called 'Urdata' in  to private repository) -
```{r eval=FALSE}
miniCRAN::addLocalPackage(pkgs = 'Urdata',pkgPath = '../../Packages Development/2018/',path= '/UrrepositoryDirectory/', build=T)
```

## Public Repository
### Github could also be used for hosting a r package repository. You could just git push your r package project into your github repository
```{shell eval=FALSE}
# adding a remote from your new repository in github
git remote add origin git@github.com:User/UserRepo.git 
git push your-local-pakcage 
```

##You may need to include the repository location in the .Rprofile so applcation like Rconnect will be able to install it
###(eg. packrat in Rconnect applications will know where to grab the package). For example - 
```{r eval= FALSE}
local({
  r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/" # exiting default repository
  r["ERMrepository"] <- "file://UrrepositoryDirectory" # for example, local private repository
  options(repos = r)
})
```





