---
title: "Package Repository"

output: html_document
---


<style type="text/css">

.main-container {
  max-width: 1200px;
  margin-left: 200px;
  margin-right: auto;
}
td {  /* Table  */
  font-size: 8px;
  
}
h1.title {
  font-size: 30px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 30px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 25px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  background: #cce5ff;
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}

ol { /* ordered list style */
    font-size: 20px;font-weight:bold;}

ul {/* dot list style */
font-size: 15px;
}


</style>




## Private Repository
### After building packages in local drive, you may want to share it within the same rstudio server or inbetween R-connect and Rstudio Server. Having a local private repository could be one of the solutions. 

* Putting devtolls package into local repository (for example, adding a package called 'Urdata' in  to private repository) -
```{r eval=FALSE}
miniCRAN::addLocalPackage(pkgs = 'Urdata',pkgPath = '../../Packages Development/2018/',path= '/UrrepositoryDirectory/', build=T)
```

## Public Repository
### Github could also be used for hosting a r package repository. You could just git push your r package project into your github repository
```{shell eval=FALSE}
# adding a remote from your new repository in github
git remote add origin git@github.com:User/UserRepo.git 
git push your-local-pakcage 
```

##You may need to include the repository location in the .Rprofile so applcation like Rconnect will be able to install it
###(eg. packrat in Rconnect applications will know where to grab the package). For example - 
```{r eval= FALSE}
local({
  r <- getOption("repos")
  r["CRAN"] <- "https://cran.rstudio.com/" # exiting default repository
  r["ERMrepository"] <- "file://UrrepositoryDirectory" # for example, local private repository
  options(repos = r)
})
```





